---
title: "courseraPack"
author: "Kevin Baktiar"
date: "2/2/2018"
output: html_document
vignette: >
  %\VignetteIndexEntry{courseraPack}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###### A package created for Coursera, using data from the US National Highway Traffic Safety Administration.
###### The data used is specific to the Fatality Analysis Reporting System. The purpose of this package is to
###### demonstrate reading in the data, what years to input, summarize the data and map out the data by state.

#### Installation

```{r echo= TRUE, results='hide'}
library(courseraPack)
```
```{r include=FALSE}
library(dplyr)
```

#### Reading in data

```{r echo=TRUE}
fars_read("accident_2013.csv.bz2")
```

#### Reads in data from a single or multiple years

```{r echo=TRUE}
years <- c(2013, 2014)
data.list <- fars_read_years(years)
data.list
```

#### Creates filename based on the year

```{r echo=TRUE}
file <- make_filename(2014)
file
```

#### Creates a summary of each year passed

```{r echo=TRUE}
years.list <- c(2013, 2014)
fars_summarize_years(years.list)
```


#### Creates graph of accidents by state

```{r echo=TRUE}
fars_map_state(1, 2013)
```
